Time for a rethink: disparity-through-time

### 2017-12-08 manuscript/time-slice.tex
Edits to acknowledgments

\begin{enumerate}
  \item Stratigraphy: time sub-samples defined by stratigraphic periods. 
  \begin{enumerate}
    \item Time bins (unequal). 
    We calculated disparity for the taxa in each stratigraphic period (age or epoch). 
    To reduce the influence of outliers on our disparity estimates, we bootstrapped each disparity measurement for each time bin by randomly resampling with replacement a new sub-sample of taxa from the observed taxa in the bin 1000 times.
    We then calculated the median disparity value for each time bin along with the 50\% and 95\% confidence intervals.
    \item Time-slices (unequal).
    We calculated disparity using our time-slicing approach with slices occurring at the midpoint of each stratigraphic period (age or epoch), and using all six time-slicing methods (acctran, deltran, random, proximity, equal splits and gradual splits).
    To reduce the influence of outliers on our disparity estimates, we bootstrapped each disparity measurement as described above for the stratigraphic time bins.
    \end{enumerate}

  \item Duration: time sub-samples defined by the duration of stratigraphic periods. 
  \begin{enumerate}
    \item Time bins (equal). 
    We calculated disparity for the taxa in each time bin where time bin size was defined by the average \textit{duration} of the stratigraphic period (age or epoch), and bootstrapped the disparity values as described above.
    \item Time-slices (unequal).
    We calculated disparity using our time-slicing approach where the interval between slices, was defined by the average \textit{duration} of the stratigraphic period (age or epoch).
    We used the six time-slicing methods and bootstrapped as described above.
  \end{enumerate}

  \item Number: time sub-samples defined by the number of stratigraphic periods. 
  \begin{enumerate}
    \item Time bins (equal). 
    We calculated disparity for the taxa in each time bin where the number of time bins was defined by the average \textit{number} of stratigraphic periods (ages or epochs) in the time frame of interest, and bootstrapped the disparity values as described above.
    \item Time-slices (unequal).
    We calculated disparity using our time-slicing approach where the number of slices, was defined by the average \textit{number} of the stratigraphic periods (ages or epochs) in the time frame of interest..
    We used the six time-slicing methods and bootstrapped as described above.
  \end{enumerate}

@@

\section{Acknowledgments}
	We thank all the PalAss folk.
  TG acknowledge support from the Australian Discovery Project Grant number DP170103227 awarded to Vera Weisbecker.

>>>>

\begin{enumerate}
  \item Stratigraphy: time sub-samples defined by stratigraphic periods. 
  \begin{enumerate}[(i)]
    \item Time bins (unequal). 
    We calculated disparity for the taxa in each stratigraphic period (age or epoch). 
    To reduce the influence of outliers on our disparity estimates, we bootstrapped each disparity measurement for each time bin by randomly resampling with replacement a new sub-sample of taxa from the observed taxa in the bin 1000 times.
    We then calculated the median disparity value for each time bin along with the 50\% and 95\% confidence intervals.
    \item Time-slices (unequal).
    We calculated disparity using our time-slicing approach with slices occurring at the midpoint of each stratigraphic period (age or epoch), and using all six time-slicing methods (acctran, deltran, random, proximity, equal splits and gradual splits).
    To reduce the influence of outliers on our disparity estimates, we bootstrapped each disparity measurement as described above for the stratigraphic time bins.
    \end{enumerate}

  \item Duration: time sub-samples defined by the duration of stratigraphic periods. 
  \begin{enumerate}[(i)]
    \item Time bins (equal). 
    We calculated disparity for the taxa in each time bin where time bin size was defined by the average \textit{duration} of the stratigraphic period (age or epoch), and bootstrapped the disparity values as described above.
    \item Time-slices (unequal).
    We calculated disparity using our time-slicing approach where the interval between slices, was defined by the average \textit{duration} of the stratigraphic period (age or epoch).
    We used the six time-slicing methods and bootstrapped as described above.
  \end{enumerate}

  \item Number: time sub-samples defined by the number of stratigraphic periods. 
  \begin{enumerate}[(i)]
    \item Time bins (equal). 
    We calculated disparity for the taxa in each time bin where the number of time bins was defined by the average \textit{number} of stratigraphic periods (ages or epochs) in the time frame of interest, and bootstrapped the disparity values as described above.
    \item Time-slices (unequal).
    We calculated disparity using our time-slicing approach where the number of slices, was defined by the average \textit{number} of the stratigraphic periods (ages or epochs) in the time frame of interest..
    We used the six time-slicing methods and bootstrapped as described above.
  \end{enumerate}

@@

\section{Acknowledgments}
	We thank Mark Sutton and Phillip Mannion for inviting us to contribute to the `Evolutionary Modelling' symposium at The Palaeontological Association Annual Meeting 2017.
  TG acknowledges support from the Australian Discovery Project Grant number DP170103227 awarded to Vera Weisbecker.
